---
title: SIGNET -- Signed Network Spectral Clustering
output: github_document:
  pandoc_args: [ "--wrap=preserve", "--columns=80" ]
bibliography: inst/REFERENCES.bib
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(SIGNET)
```

[![GitHub R package version](https://img.shields.io/github/r-package/v/zongyue-teng/SIGNET?label=R%20in%20dev&color=green)](https://github.com/zongyue-teng/SIGNET/blob/main/DESCRIPTION)
[![GitHub last commit](https://img.shields.io/github/last-commit/zongyue-teng/SIGNET)](https://github.com/zongyue-teng/SIGNET/commits/main)
[![R-CMD-check](https://github.com/zongyue-teng/SIGNET/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/zongyue-teng/SIGNET/actions/workflows/R-CMD-check.yaml)
[![GitHub License](https://img.shields.io/github/license/zongyue-teng/SIGNET?color=blue)](https://github.com/zongyue-teng/SIGNET/blob/main/LICENSE.md)

The $\mathtt{SIGNET}$ package intends to be a user-friendly package implementing a spectral clustering algorithm for signed networks. 

## Features

The package provides functions to 

1. implement signed network clustering;
2. select the number of clusters in a data-driven manner;
3. enable high-dimensional biological network analysis.


## Installation

You can install the $\mathtt{SIGNET}$ package from GitHub with:

```{r install_pkg, eval = FALSE} 
# install.packages("devtools")
devtools::install_github("zongyue-teng/SIGNET")
```

## Reference {-}
